### 2025-06-19 basic-statistics.qmd
20250618 - fix formulas

$$
\begin{aligned}
  d &= \frac{\text{mean difference}}{\text{pooled standard deviation}} \\
   &= \frac{\bar{X_1} - \bar{X_2}}{s} \\
\end{aligned}
$$ {#eq-cohensD}

where:

>>>>

$$
\begin{aligned}
  d &= \frac{\text{mean difference}}{\text{pooled standard deviation}} \\
   &= \frac{\bar{x_1} - \bar{x_2}}{s} \\
\end{aligned}
$$ {#eq-cohensD}

where $\bar{x_1}$ and $\bar{x_2}$ is the mean for group 1 and group 2, respectively, and:
